Tool-driven Revolutions in Archaeological Science

### 2019-10-16 analysis/paper/jcaa-paper.Rmd
by -> sep in data input & cleaning, update ctv data

# this is a hand-collected spreadsheet of the total number 
# articles published in these journals. We get these from Web
# of Science 'publication name' search
top_journals_for_cran_cites_articles_per_year <-
  read_csv(str_glue('{here::here()}/analysis/data/raw_data/top_journals_for_cran_cites_articles_per_year.csv')) %>%
  select(-X1) %>%
  gather(variable, value, -year) %>%
  separate(variable,
           into = str_glue('X{1:4}'),
           by = "_") %>%
  select(year, X4, value) %>% 
  mutate(year = as.integer(year)) %>% 
  rename( "journalname" = "X4", 
          'PY' = "year")

>>>>

# this is a hand-collected spreadsheet of the total number 
# articles published in these journals. We get these from Web
# of Science 'publication name' search
top_journals_for_cran_cites_articles_per_year <-
  read_csv(str_glue('{here::here()}/analysis/data/raw_data/top_journals_for_cran_cites_articles_per_year.csv')) %>%
  select(-X1) %>%
  gather(variable, value, -year) %>%
  separate(variable,
           into = str_glue('X{1:4}'),
           sep = "_") %>%
  select(year, X4, value) %>% 
  mutate(year = as.integer(year)) %>% 
  rename( "journalname" = "X4", 
          'PY' = "year")
